Energy and exergy analysis of a cruise ship

### 2017-07-11 Manuscript/Manuscript.tex
Modifications to the .py files - STABLE VERSION
Almost everything is included. Most bugs have been fixed. The whole thing kind of works!

The corresponding ditributions are presented in Figure \ref{fig:Tsea_hist}

@@

Figure \ref{fig:vship_hist} represents the distribution of the ship speed, both in terms of statistical distribution and in terms of a reference 24h period. The ship operates almost for the entire year according to a fix schedule.

@@

\begin{itemize}
	\item External temperature
	\item Sea water temperature
	\item Ship speed
\end{itemize}

The results are presented in two main forms:
\begin{itemize}
	\item Time series (comparing some relevant trips with a daily time scale)
	\item Distribution plot (or box plot...box plots are easier to compare, distribution plots are easier to interpret)
\end{itemize}

@@

@@

The figure also shows the operation of validation of the assumptions by comparison of the measured values for the boilers fuel consumption (here translated into an energy-per-day basis to ease the comparison). It should be noted that, although the absolute value is still quite different compared to the calculated one (mean error is 255\%, minimum 3\%), there is evidence that the order of magnitude is similar, and that some trends are followed

>>>>

The corresponding distributions are presented in Figure \ref{fig:Tsea_hist}

@@

Figure \ref{fig:vship_hist} represents the distribution of the ship speed, both in terms of statistical distribution and in terms of a reference 24h period. The ship operates almost for the entire year according to a fix schedule, while there are a couple of periods (particularly during the summer months) when the ship operates at higher speed. This can also be seen from Figure \ref{fig:Pme_vs_vship}, where the main cluster of operations at middle-low speed can be clearly identified, as well as the smaller area of operations at high speed.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/Pme_vs_vship}
	\caption{Scatter plot, Propulsion power versus ship speed}
	\label{fig:Pme_vs_vship}
\end{figure}

@@

Here we can see the typical example (note: the day was not selected as "typical", but simply randomly) of the energy demand during a winter and a summer day (Figures \ref{fig:Demand_vs_time_W} and \ref{fig:Demand_vs_time_S}).

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/Demand_vs_time_W}
	\caption{Energy demand during a day of operations, Winter}
	\label{fig:Demand_vs_time_W}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/Demand_vs_time_S}
	\caption{Energy demand during a day of operations, Summer}
	\label{fig:Demand_vs_time_S}
\end{figure}

@@

The figure also shows the operation of validation of the assumptions by comparison of the measured values for the boilers fuel consumption (here translated into an energy-per-day basis to ease the comparison). It should be noted that, although the absolute value is still quite different compared to the calculated one (mean error is 255\%, minimum 3\%), there is evidence that the order of magnitude is similar, and that some trends are followed.
